### 2022-08-04 main/chapter_2ljets.tex
which/that, improve matrix method non-prediction paragraph

Yes, actual data are histogrammed in the Matrix Method, and those data include
tight-tight events which comprise the data of our search regions, and those
are the same data in which we are searching for anomalous signals.
Since it includes actual data, this method unblinds all regions,
including signal regions, early.
And because it knows the data we are supposed to be predicting, it is no
prediction at all!

>>>>

Yes, actual data are histogrammed in the Matrix Method, and those data include
tight-tight events that comprise the data of our search regions, the very same
data in which we are searching for anomalous signals.
Since it includes actual data, this method unblinds all regions,
including signal regions, early.
And because it knows and uses the data we are supposed to be predicting, it is
no prediction at all!
